Conference output

### 2018-05-28 Report/arne-conference.Rmd
Fixes ylab

```{r setup, include=FALSE}
library(ggplot2)
library(dplyr)
source('../Scripts/analysis-helpers.R')
sop_all <- read.table("../sop.csv", sep=";", header = T, stringsAsFactors = F)
walk_all <- read.table("../walk.csv", sep=";", header = T, stringsAsFactors = F)
```

@@

MEasure of overall sum of errors. Mean columns define mean sum of errors for all participants in that block
```{r, warnings = F}
df <- block_measure(condition_all_sums, "sum.errors")
df
ggplot(melt(df[,1:4]), aes(x = condition, y = value, fill = variable)) + geom_bar(stat = 'identity', position="dodge") + ylab("Mean number of mistakes")

@@

Measure of mean distance. First three columns define mean normalised distance in each block.
```{r, warnings = F}
df <- block_measure(condition_all_sums, "mean.distance")
df
ggplot(melt(df[,1:4]), aes(x = condition, y = value, fill = variable)) + geom_bar(stat = 'identity', position="dodge") + ylab("Mean number of mistakes")

>>>>

```{r setup, include=FALSE}
library(ggplot2)
library(dplyr)
library(reshape2)
source('../Scripts/analysis-helpers.R')
sop_all <- read.table("../sop.csv", sep=";", header = T, stringsAsFactors = F)
walk_all <- read.table("../walk.csv", sep=";", header = T, stringsAsFactors = F)
```

@@

MEasure of overall sum of errors. Mean columns define mean sum of errors for all participants in that block
```{r, echo=F, warnings = F}
df <- block_measure(condition_all_sums, "sum.errors")
df
ggplot(melt(df[,1:4]), aes(x = condition, y = value, fill = variable)) + geom_bar(stat = 'identity', position="dodge") + ylab("Mean number of mistakes")

@@

Measure of mean distance. First three columns define mean normalised distance in each block.
```{r, echo=F, warnings = F}
df <- block_measure(condition_all_sums, "mean.distance")
df
ggplot(melt(df[,1:4]), aes(x = condition, y = value, fill = variable)) + geom_bar(stat = 'identity', position="dodge") + ylab("Mean normalised distance")
